ArKanjo: a tool for detecting function-level Code Duplication in the Linux Kernel

### 2025-07-01 paper/paper.tex
Fix the simplest points from revision
It is missing:
- the url.
- the textfile with the accepted patches.
- information about speed.
- future works (maybe)

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The Linux kernel massive scale (+28 M LoC, +20 K contributors) presents unique 
maintenance challenges. Surprisingly, code duplication remains a persistent issue 
in the kernel codebase, which can hinder its evolution and patching. Academic 
approaches often focus on pairwise comparison of code artifacts, which are not directly applied 
to comprehensive codebase analyses. Other existing free
software\footnote{In this paper, we use the term \textit{Free Software}
interchangeably with \textit{Open Source Software}.} tools explored in 
practice frequently suffer from limited functionality, such as primitive textual 
matching, prove too narrow in scope, or fail to deliver effective results on complex, 
large-scale codebases. Existing solutions generally fail to address the Linux kernel 
specific needs: (1) scalability to handle its size, (2) actionable results for 
developers, and (3) integration with kernel development workflows.
%
This paper presents \textit{ArKanjo}, a novel command-line tool for Linux kernel maintenance 
designed to detect and analyze function-level duplications. Released under the MIT 
license, ArKanjo employs a two-stage architecture consisting of a Preprocessor and 
a Query Responder that separates computationally intensive analysis from efficient 
querying for duplications within large codebases. Pivotal advantages of ArKanjo over 
existing solutions include: (1) optimization for C codebases with kernel-specific 
patterns; (2) preprocessing that enables rapid queries without redundant analysis; 
and (3) prioritization of duplicates that impact maintainability, such as copied 
buggy logic. 
%
We evaluate ArKanjo against real-world duplication cases in recent 
kernel versions, demonstrating its effectiveness in identifying problematic clones 
that generic tools often overlook. By identifying well-defined, manageable 
duplication instances, ArKanjo effectively lowers the barrier for new contributors, 
a capability evidenced by its role in guiding students to make their first code 
improvements to the kernel. ArKanjo offers immediate value to kernel maintainers 
and serves as a replicable model for clone detection in other large-scale free 
software projects.

@@

The Function Parser receives the input codebase and transforms it into the temporary
codebase. It iterates through every source code file written in a supported programming 
language and uses a language-specific extractor to isolate each function. For each extracted 
function, two new source code files and a metadata file are created in the temporary codebase, 
represented by the pair \textbf{$<$file name, function name$>$}, the source code of the function, 
and the function metadata. One of the new files contains the function body, and the other 
contains the function signature. The metadata file includes additional relevant information,
such as the function name, the line where the signature starts, and the line where the function 
body ends. Currently, the supported programming languages are C and Java, although Java support is limited.

@@

Unlike state-of-the-art methods, our tool does not distinguish between clone types and
identifies duplications at the function level rather than the file level, which is typical in
state-of-the-art tools. Therefore, we adapted the metric calculation method for evaluation
purposes. Specifically, we considered every pair of functions with a similarity metric
equal to or greater than a threshold $X$ as duplicates and marked the corresponding file
pairs. A correctly identified duplication pair is counted as accurate for its clone type, while
an incorrectly inferred pair is considered incorrect across all clone types.
To understand the impact of varying the similarity threshold, we evaluated our tool using
different threshold values: 30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, and 100\%. We then analyzed
and discussed the results.

@@

Using the ArKanjo tool, the main author and 26 students (divided into 12 groups) identified and refactored duplicated code in the AMD Display driver and the Industrial I/O (IIO) subsystems, submitting their work 
as patches to the community maintainers. This effort resulted in 13 patch submissions: 
One was from the main author to the AMD Display driver, and 12 were from the student groups, with 11 targeting 
the IIO subsystem and one aimed at the AMD Display driver. After a lengthy review process, the main author's patch was successfully accepted and merged into the kernel, removing over 500 lines of duplicated code.

The student efforts demonstrated that newcomers could use the tool to contribute effectively. 
Of the 12 student patches, five were accepted, four were rejected, and three required follow-up 
fixes based on maintainer feedback. To remove the duplicated code, seven student groups used the 
\textit{Parameterize Method}, and two used the \textit{Extract Method} \cite{refactorbook}, both of which are 
straightforward refactoring strategies. These results support the conclusion that ArKanjo identifies 
actionable duplications and that newcomers can successfully contribute patches to the kernel.

@@

This paper presented ArKanjo, a novel tool designed to detect effectively 
and facilitate the refactoring of function-level code duplication within the Linux kernel. 
Evaluations demonstrated that ArKanjo is highly effective at identifying Type-1 and Type-2 
clones, which are often indicative of propagated issues such as copied buggy logic. We validated the practical 
value of the tool through an ethnographic study in which the main author and student 
groups used ArKanjo to identify actionable duplications. This effort led to 13 patch 
submissions, including one from the main author that removed over 500 lines of code and merged 
into the kernel, alongside five successful student contributions at this moment. While some refactoring 
efforts were declined due to maintainer priorities, ArKanjo successfully lowered the barrier 
for new contributors to make meaningful improvements. The tool provides immediate value for 
kernel maintenance and serves as a model for clone detection in other large-scale projects.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The Linux kernel massive scale (+28 M LoC, +20 K contributors) presents unique 
maintenance challenges. Surprisingly, code duplication remains a persistent issue 
in the kernel codebase, which can hinder its evolution and patching. Academic 
approaches often focus on pairwise comparison of code artifacts, which are not directly applied 
to comprehensive codebase analyses. Other existing free
software\footnote{In this paper, we use the term \textit{Free Software}
interchangeably with \textit{Open Source Software}.} tools explored in 
practice frequently suffer from limited functionality, such as primitive textual 
matching, prove too narrow in scope, or fail to deliver effective results on complex, 
large-scale codebases. Existing solutions generally fail to address the Linux kernel 
specific needs: (1) scalability to handle its size, (2) actionable results for 
developers, and (3) integration with kernel development workflows.
%
This paper presents \textit{ArKanjo}, a novel command-line tool for Linux kernel maintenance 
designed to detect and analyze function-level duplications. Released under the MIT 
license, ArKanjo employs a two-stage architecture consisting of a Preprocessor and 
a Query Responder that separates computationally intensive analysis from efficient 
querying for duplications within large codebases. Pivotal advantages of ArKanjo over 
existing solutions include: (1) preprocessing that enables rapid queries without redundant analysis; 
and (2) prioritization of duplicates that impact maintainability, such as copied 
buggy logic. 
%
We evaluate ArKanjo against real-world duplication cases in recent 
kernel versions, demonstrating its effectiveness in identifying problematic clones 
that generic tools often overlook. By identifying well-defined, manageable 
duplication instances, ArKanjo effectively lowers the barrier for new contributors, 
a capability evidenced by its role in guiding students to make their first code 
improvements to the kernel. ArKanjo offers immediate value to kernel maintainers 
and serves as a replicable model for clone detection in other large-scale free 
software projects.

@@

The Function Parser receives the input codebase and transforms it into the temporary
codebase. It iterates through every source code file written in a supported programming 
language and uses a language-specific extractor to isolate each function. For each extracted 
function, two new source code files and a metadata file are created in the temporary codebase, 
represented by the pair \textbf{$<$file name, function name$>$}, the source code of the function, 
and the function metadata (in practice, this is a duplication of the original codebase, 
structured as a parsed representation). One of the new files contains the function body, and the other 
contains the function signature. The metadata file includes additional relevant information,
such as the function name, the line where the signature starts, and the line where the function 
body ends. Currently, the supported programming languages are C and Java, although Java support is limited.

@@

Unlike state-of-the-art methods, our tool does not distinguish between clone types. 
Additionally, it identifies duplications at the function level, whereas most existing 
tools operate at the file level.
Therefore, we adapted the metric calculation method for evaluation
purposes. Specifically, we considered every pair of functions with a similarity metric
equal to or greater than a threshold $X$ as duplicates and marked the corresponding file
pairs. A correctly identified duplication pair is counted as accurate for its clone type, while
an incorrectly inferred pair is considered incorrect across all clone types.
To understand the impact of varying the similarity threshold, we evaluated our tool using
different threshold values: 30\%, 40\%, 50\%, 60\%, 70\%, 80\%, 90\%, and 100\%. We then analyzed
and discussed the results.

@@

Using the ArKanjo tool, the main author and 23 students (divided into 11 groups) identified and refactored 
duplicated code in the AMD Display driver and the Industrial I/O (IIO) subsystems, submitting their work 
as patches to the community maintainers. This effort resulted in 12 patch submissions: 
One was from the main author to the AMD Display driver, and 11 were from the student groups, with 10 targeting 
the IIO subsystem and one aimed at the AMD Display driver. After a lengthy review process, the main author's patch 
was successfully accepted and merged into the kernel, removing over 500 lines of duplicated code.

The student efforts demonstrated that newcomers could use the tool to contribute effectively. 
Of the 11 student patches, five were accepted, four were rejected, and three required follow-up 
fixes based on maintainer feedback. To remove the duplicated code, seven student groups used the 
\textit{Parameterize Method}, and two used the \textit{Extract Method} \cite{refactorbook}, both of which are 
straightforward refactoring strategies. These results support the conclusion that ArKanjo identifies 
actionable duplications and that newcomers can successfully contribute patches to the kernel.

@@

This paper presented ArKanjo, a novel tool designed to detect effectively 
and facilitate the refactoring of function-level code duplication within the Linux kernel. 
Evaluations demonstrated that ArKanjo is highly effective at identifying Type-1 and Type-2 
clones, which are often indicative of propagated issues such as copied buggy logic. We validated the practical 
value of the tool through an ethnographic study in which the main author and student 
groups used ArKanjo to identify actionable duplications. This effort led to 13 patch submissions, 
including one from the main author and five from student groups that were successfully merged into 
the kernel, collectively removing 991 lines of duplicated code. While some refactoring 
efforts were declined due to maintainer priorities, ArKanjo successfully lowered the barrier 
for new contributors to make meaningful improvements. The tool provides immediate value for 
kernel maintenance and serves as a model for clone detection in other large-scale projects.
